---
title: "FARS Functions"
author: "Dmitri Brengauz"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FARS Functions}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}     
---

Some basic functions for working with Fars data.

## File Utilities
To read a database compressed file intto a tible, use the `fars_read` function:
```{r, error=TRUE}
fars_read("/data/accident_2014.csv.bz2")
```

The two functions `make_filename` and `fars_read_years` are helper
functions that don't do anything interesting on their
own. `make_filename` will return a properly formatted FARS database
file, while `fars_read_years` will return a  30,056 x 2 tibble of
months and years for each obeservation, useful for sorting data.

## Summary Utilities

### `fars_summarize` 
Return a per-month total of accidents for that year:

```{r, warning=FALSE}
fars_summarize_years(c(2014,2015))
```

###  `fars_map_state`
```{r warning=FALSE}
fars_map_state(c(1,4,5),2014)
```

shows a plot of the accidents in Alabama, Arizona, and Arkansas in
the year 2014.

### Bugs
Alaska does not work.
